---
title: "Bootstrapping"
output: github_document
---

```{r setup, include = FALSE, message = FALSE, warning=FALSE}
library(tidyverse)
library(modelr)
library(p8105.datasets)

knitr::opts_chunk$set(
  echo = TRUE,
  warning = FALSE,
  fig.width = 6,
  fig.asp = .6,
  out.width = "90%"
)

theme_set(theme_minimal() + theme(legend.position = "bottom"))

options(
  ggplot2.continuous.colour = "viridis",
  ggplot2.continuous.fill = "viridis"
)

scale_colour_discrete = scale_color_viridis_d
scale_fill_discrete = scale_fill_viridis_d
```

## Simulate data

```{r}
n_samp = 250

sim_df_const =
  tibble(
    x = rnorm(n_samp, 1, 1),
    error = rnorm(n_samp, 0, 1),
    y = 2 + 3 * x + error
  )

sim_df_nonconst = 
  sim_df_const %>%
  mutate(
    error = error * .75 * x,
    y = 2 + 3 * x + error
  )

```

Plot the datasets

```{r}
sim_df_const %>%
  ggplot(aes(x = x, y = y)) +
  geom_point() +
  geom_smooth(method = "lm")

sim_df_nonconst %>%
  ggplot(aes(x = x, y = y)) +
  geom_point() +
  geom_smooth(method = "lm")
```

```{r}
lm(y ~ x, data = sim_df_const) %>% broom::tidy()
lm(y ~ x, data = sim_df_nonconst) %>% broom::tidy()
```


## Draw one bootstap sample

```{r}
boot_sample = function(df) {
  
  sample_frac(df, replace = TRUE) %>%
    arrange(x)
  
}
```

Check if this works ..


```{r}
boot_sample(sim_df_nonconst) %>%
  ggplot(aes(x = x, y = y)) +
  geom_point(alpha = .3) +
  geom_smooth(method = "lm") +
  ylim(-5, 16)
```

```{r}
boot_sample(sim_df_nonconst) %>%
  lm(y ~ x, data = .) %>%
  broom::tidy()
```


## Many samples and analysis

```{r}
boot_straps = 
  tibble(
    strap_number = 1:1000,
    strap_sample = rerun(1000, boot_sample(sim_df_nonconst))
  )
```

Can I run my analysis on these ...?

```{r}
boot_results = 
  boot_straps %>%
  mutate(
    models = map(.x = strap_sample, ~lm(y ~ x, data = .x)),
    results = map(models, broom::tidy)
  ) %>%
  select(strap_number, results) %>%
  unnest(results)
```

What do I have now?

```{r}
boot_results %>%
  group_by(term) %>%
  summarize(
    mean_est = mean(estimate),
    sd_est = sd(estimate)
  )
```

Look at the distributions

```{r}
boot_results %>%
  filter(term == "x") %>%
  ggplot(aes(x = estimate)) +
  geom_density()
```

Construct bootstrap CI

```{r}
boot_results %>%
  group_by(term) %>%
  summarize(
    ci_lower = quantile(estimate, 0.025),
    ci_upper = quantile(estimate, 0.975)
  )
```


## Bootstrap using modelr

Can we simplify anything ...?

```{r}
sim_df_nonconst %>%
  bootstrap(1000, id = "stap_number") %>%
  mutate(
    models = map(.x = strap, ~lm(y ~ x, data = .x)),
    results = map(models, broom::tidy)
  ) %>%
  select(stap_number, results) %>%
  unnest(results) %>%
  group_by(term) %>%
  summarize(
    mean_est = mean(estimate),
    sd_est = sd(estimate)
  )
```

## Revisit nyc airbnb

```{r}
data("nyc_airbnb")

nyc_airbnb = 
  nyc_airbnb %>%
  mutate(stars = review_scores_location / 2) %>%
  rename(
    borough = neighbourhood_group
  ) %>%
  filter(borough != "Staten Island") %>%
  select(price, stars, borough, neighbourhood, room_type)
```

```{r}
nyc_airbnb %>%
  ggplot(aes(x = stars, y = price)) +
  geom_point()
```

```{r}
nyc_airbnb %>%
  filter(borough == "Manhattan") %>%
  drop_na(stars) %>%
  ggplot(aes(x = stars, y = price)) +
  geom_point()
```
We got clearly non-constant variance in the relationship between stars and price and a few outliers, so we would like to do to get the standard error for the linear model here bootstrap - take a sample with replacement, fit a regression of price against stars and save the estimated intercept and slope each time.

```{r}
airbnb_boot_results = 
  nyc_airbnb %>%
  filter(borough == "Manhattan") %>%
  drop_na(stars) %>%
  bootstrap(1000, id = "stap_number") %>%
  mutate(
    models = map(.x = strap, ~lm(price ~ stars, data = .x)),
    results = map(models, broom::tidy)
  ) %>%
  select(stap_number, results) %>%
  unnest(results)
  
airbnb_boot_results %>%
  group_by(term) %>%
  summarize(
    mean_est = mean(estimate),
    sd_est = sd(estimate)
  )
```

Compare this to `lm`

```{r}
nyc_airbnb %>%
  filter(borough == "Manhattan") %>%
  drop_na(stars) %>%
  lm(price ~ stars, data = .) %>%
  broom::tidy()
```

Look at the distributions

```{r}
airbnb_boot_results %>%
  filter(term == "stars") %>%
  ggplot(aes(x = estimate)) +
  geom_density()
```

Construct bootstrap CI

```{r}
airbnb_boot_results %>%
  group_by(term) %>%
  summarize(
    ci_lower = quantile(estimate, 0.025),
    ci_upper = quantile(estimate, 0.975)
  )
```

